<<<<<<< HEAD
---
title: "Report for PS 1"
author:
- Yukai Yang
- Another Author
- Riccardo 2
date: ""
output:
  html_document:
    df_print: paged
  df_print: kable
  pdf_document:
    keep_tex: yes
toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(FE)
```


##  B: Dynamical properties of financial return series

```{r setupb, include=F}
data = index_d
```

```{r}
# calculating autocorrelations
lret = apply(log(data),2,diff)
summary(lret)
matplot(lret,type='l',ylab='log returns',xlab='time horizon')

sum(is.na(lret[,'FRCAC40']))
# plotting Auto correlation for each column, removing missing values
par(mfrow = c(3,3))
for(tmp in 1:7){
  colnames(lret)[tmp]; acf(lret[!is.na(lret[,tmp]),tmp])
}
# if we want the values instead of the plots
cors <- matrix(NA, nrow = 10, ncol = 7)  

# Loop over each column in lret
for(tmp in 1:7){
  # Get the column name
  colnames(lret)[tmp]
  
  # Calculate ACF values without plotting
  acf_result <- acf(lret[!is.na(lret[,tmp]), tmp], plot = FALSE)
  
  # Store the first 10 lags of the ACF in the `cors` matrix
  cors[, tmp] <- acf_result$acf[2:11]  # Excluding the 0th lag (correlation with itself)
}
# first ten autocorrelations:
cors

```

```{r}
LB <- function(vx,lag,ip){
  tmp = acf(vx,lag.max=lag,plot=F)$acf
  tmp = tmp[2:(lag+1)]**2
  test = sum(tmp/(length(vx)-1:lag))*length(vx)*(length(vx)+2)
  return(list(test=test, pval=1-pchisq(test,df=lag-ip)))
}

tmp = 6

LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=10,ip=0)
LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=50,ip=0)
LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=100,ip=0)



```

```{r}
# pairwise cross autocorrelations between individual return series
# choose a pair
pair = c(3,7)
mx = lret[394:dim(lret)[1],pair]
mx = lret[,pair]
cor(mx,use="complete.obs")
cor(mx[2:dim(mx)[1],], mx[1:(dim(mx)[1]-1),],use="complete.obs")
acf(lret[394:dim(lret)[1],pair])
pacf(lret[394:dim(lret)[1],pair])

# generate squared log returns. Analyze their dynamical properties. What do you find? 
lret2 = lret^2

tmp = 7; colnames(lret2)[tmp]; acf(lret2[!is.na(lret2[,tmp]),tmp])
```

=======
---
title: "Report for PS 1"
author:
- Yukai Yang
- Riccardo
date: ""
output:
  html_document:
    df_print: paged
  df_print: kable
  pdf_document:
    keep_tex: yes
toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(FE)
```


##  B: Dynamical properties of financial return series

```{r setupb, include=F}
data = index_d
```

```{r}
# calculating autocorrelations
lret = apply(log(data),2,diff)
summary(lret)
matplot(lret,type='l',ylab='log returns',xlab='time horizon')

sum(is.na(lret[,'FRCAC40']))
# plotting Auto correlation for each column, removing missing values
par(mfrow = c(3,3))
for(tmp in 1:7){
  colnames(lret)[tmp]; acf(lret[!is.na(lret[,tmp]),tmp])
}
# if we want the values instead of the plots
cors <- matrix(NA, nrow = 10, ncol = 7)  

# Loop over each column in lret
for(tmp in 1:7){
  # Get the column name
  colnames(lret)[tmp]
  
  # Calculate ACF values without plotting
  acf_result <- acf(lret[!is.na(lret[,tmp]), tmp], plot = FALSE)
  
  # Store the first 10 lags of the ACF in the `cors` matrix
  cors[, tmp] <- acf_result$acf[2:11]  # Excluding the 0th lag (correlation with itself)
}
# first ten autocorrelations:
cors

```

```{r}
LB <- function(vx,lag,ip){
  tmp = acf(vx,lag.max=lag,plot=F)$acf
  tmp = tmp[2:(lag+1)]**2
  test = sum(tmp/(length(vx)-1:lag))*length(vx)*(length(vx)+2)
  return(list(test=test, pval=1-pchisq(test,df=lag-ip)))
}

tmp = 6

LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=10,ip=0)
LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=50,ip=0)
LB(vx=lret[!is.na(lret[,tmp]),tmp],lag=100,ip=0)



```

```{r}
# pairwise cross autocorrelations between individual return series
# choose a pair
pair = c(3,7)
mx = lret[394:dim(lret)[1],pair]
mx = lret[,pair]
cor(mx,use="complete.obs")
cor(mx[2:dim(mx)[1],], mx[1:(dim(mx)[1]-1),],use="complete.obs")
acf(lret[394:dim(lret)[1],pair])
pacf(lret[394:dim(lret)[1],pair])

# generate squared log returns. Analyze their dynamical properties. What do you find? 
lret2 = lret^2

tmp = 7; colnames(lret2)[tmp]; acf(lret2[!is.na(lret2[,tmp]),tmp])
```

>>>>>>> 419cee2fdc72fd24be58481cfff76577ac1bacff
