---
title: "Report for PS 1"
author:
- Yukai Yang
- Another Author
date: ""
output:
  html_document:
    df_print: paged
  df_print: kable
  pdf_document:
    keep_tex: yes
toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("yukai-yang/FE")
library(tidyverse)
library(FE)
library("plotly")
library(psych)
library("tibble")
library("ggplot2")
```

#  Statistical Properties of Asset Returns

## Plot the series of log returns and compute descriptive statistics. Which distributional properties do you find? Do you find differences between daily and weekly data?

Time series plots:
```{r PLOT1, echo=F}
ggplot(DJ_d, aes(y=r_Dow_Jones,x=1:nrow(DJ_d))) + geom_line() +
  labs(x='time horizon',y='daily log return')
```

```{r PLOT1, echo=F}
ggplot(DJ_w, aes(y=r_close,x=1:nrow(DJ_w))) + geom_line() +
  labs(x='time horizon',y='daily log return')
```

```{r PLOT2, echo=F}
ggplot(DJ_d, aes(r_Dow_Jones)) + geom_density()
ggplot(DJ_d, aes(r_Dow_Jones)) + geom_histogram(binwidth=.002)

```

```{r PLOT2, echo=F}
ggplot(DJ_w, aes(r_close)) + geom_density()
ggplot(DJ_w, aes(r_close)) + geom_histogram(binwidth=.002)

```

```{r descr, echo=F}
describe(DJ_d$r_Dow_Jones)
describe(DJ_w$r_close)
```
Evaluate using qq plots:
```{r}
ggplot(DJ_d) + geom_qq(aes(sample=r_Dow_Jones/sd(r_Dow_Jones))) +
  geom_abline(aes(intercept=0,slope=1),color="red")
ggplot(DJ_w) + geom_qq(aes(sample=r_close/sd(r_close))) +
  geom_abline(aes(intercept=0,slope=1),color="red")
```


## Evaluate the empirical distributions of the index log returns using quantile-quantile plots (QQ-plots). Test the empirical distribution against

### a) a normal distribution (with same mean and variance),

Check the earlier plots



### b) alternative tn-distributions with n degrees of freedom.

Here we check the empirical distribution of the data to a t distribution with 3 degrees of freedom. 

```{r tdist}
df = 3
tmp = ggplot(DJ_d, aes(sample=r_Dow_Jones/sd(r_Dow_Jones)*sqrt(df/(df-2))))
tmp + geom_qq(distribution=stats::qt, dparams=list(df=df)) + geom_abline(aes(intercept=0,slope=1),color="red")
#qqplot(rt(length(DJ_d$r_Dow_Jones),df=5),DJ_d$r_Dow_Jones)
```


## 3) Compute a x2-goodness-of-fit test against

```{r good, include=F}
#prep for the plots
#vdata = DJ_d$r_Dow_Jones
vdata = DJ_w$r_close
vdata = (vdata - mean(vdata))/sd(vdata)
ik = 20
grids = 1:ik/ik
```

### a) a normal distribution

We want to see if the data fits a normal distribution.
```{r gooda}
vq = pnorm(vdata)
hist(vq, breaks = 20, main = "probs of log returns",
     xlab = "vq", col = "skyblue", border = "white")
vn = NULL; for(val in grids) vn = c(vn,sum(vq <= val))
vn = c(vn[1],diff(vn))
test = sum((vn-length(vdata)/ik)**2/(length(vdata)/ik))
cat("test =",test," df =",ik-3," p-value =",1-pchisq(test,df=ik-3))
```
Conclusion, no it does not.

### b) a tn-distribution with n degrees of freedom,

We test if the data fits a t-distribution:
```{r goodb}
df = 3
ndata = vdata*sqrt(df/(df-2))
vq = pt(ndata,df=5); hist(vq)
vn = NULL; for(val in grids) vn = c(vn,sum(vq <= val))
vn = c(vn[1],diff(vn))
test = sum((vn-length(vdata)/ik)**2/(length(vdata)/ik))
cat("test =",test," df =",ik-3," p-value =",1-pchisq(test,df=ik-3))
```

We conclude that it does not, but the fit is better than a normal distribution.

### c) a mixture of normal distributions with mixture probability alpha and variance sigma2

Now we try and fit 

```{r}
alpha = 0.1514736
sigma = 4.0013995
ndata = vdata * sqrt((1-alpha) + alpha*sigma**2)
vq = (1-alpha)*pnorm(ndata) + alpha*pnorm(ndata,sd=sigma); hist(vq)
vn = NULL; for(val in grids) vn = c(vn,sum(vq <= val))
vn = c(vn[1],diff(vn))
test = sum((vn-length(vdata)/ik)**2/(length(vdata)/ik))
cat("test =",test," df =",ik-3," p-value =",1-pchisq(test,df=ik-3))
```

The fit is better

Write a function for minimization to choose the optimal pair for $\alpha$ and $\sigma$.

```{r}
func <- function(vx){
  alpha = vx[1]
  sigma = vx[2]
  ndata = vdata*sqrt((1-alpha) + alpha*sigma**2)

  vq = (1-alpha)*pnorm(ndata) + alpha*pnorm(ndata,sd=sigma)
  vn = NULL; for(val in grids) vn = c(vn,sum(vq <= val))
  vn = c(vn[1],diff(vn))
  return(sum((vn-length(vdata)/ik)**2/(length(vdata)/ik)))
}

func(c(0.15,4))

```


```{r}

optim(par=c(0.15,4),fn=func,method="BFGS")
optim(par=c(0.17,3.7),fn=func,method="L-BFGS-B",lower=c(0,0),upper=c(1,10))

```



```{r, cache=T}
atmp = seq(from=0.05, to=.95, length.out=40)
stmp = seq(from=1, to=10, length.out=50)
tmp = expand.grid(atmp,stmp)
res = apply(tmp,1,func)
res = t(matrix(res, nrow=length(atmp)))

ret = plot_ly(x=atmp, y=stmp, z=res) %>% add_surface() %>%
  layout(scene=list(xaxis=list(title='alpha'), yaxis=list(title='sigma'), zaxis=list(title='function')))
ret
```

